Generative AI for Image Reconstruction with Intensity Interferometry: A First Attempt

### 2024-12-09 Phase_II/draft/GAN.tex
modification

\section{Generative Adversarial Networks}
In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs). The concept is rather simple, as it consists of two competing networks. The first network is called a generator and creates new images based on an input image. Here, for consistency, the images generated by the generator will be denoted as generated images. The second network is the discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \citep{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

The goal is now to learn the distribution of the generator $p_g$ over the data $x$. We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$. $G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \citep{goodfellow2014generative}. The problem can be reformulated as: 

@@

where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator and is expressed as

@@

It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \citep{goodfellow2014generative}.

@@

	\caption{Generator and discriminator losses for three different learning rates. The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss. There is no significant difference, but the highest learning rate might be prone to outliers. }

@@

	\caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers. Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}

@@

		\caption{Discriminator loss for different discriminator training.}

@@

		\caption{Generator losses for different discriminator training.}

@@

	\caption{The amount of discriminator training has a high impact on the discriminator score. The discriminator repetition indicates the factor by which the discriminator is trained more with respect to the generator.}

@@

	\caption{The number of telescopes has a very impact on the model performance. If there are only two telescopes (1 baseline), both discriminator and generator are not trained smoothly: One gains a big advantage over the other. The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}

@@

Later, GAN extended its version to a conditional model \citep{mirza2014conditional}. In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:

@@

Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth. Hence, the function that is minimized as:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(G)$ is given as
\begin{equation}
	\centering
	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}

@@

\subsection{Generator}
The used generator in this paper is a common U-Net convolutional network \citep{ronneberger2015u}. It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged. The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers. The expansion consists of repeated convolution, batch normalization, and ReLU layers. The first contracting step also includes a dropout layer \citep{isola2017image}.

\subsection{Discriminator}
The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake. The overall result is then estimated based on the average. The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \citep{isola2017image}.

>>>>

\section{Generative Adversarial Networks}

In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs). The concept is rather simple, as it consists of two competing networks. The first network is called a Generator and creates new images based on an input image. Here, for consistency, the images generated by the Generator will be denoted as generated images. The second network is the Discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \cite{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

The goal is now to learn the distribution of the Generator $p_g$ over the data $x$. We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$. $G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \cite{goodfellow2014generative}. The problem can be reformulated as: 

@@

where $D^{*}_{G}$ denotes the optimum of the Discriminator for a given fixed Generator and is expressed as

@@

It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.

@@

	\caption{Generator and Discriminator losses for three different learning rates. The upper figure shows the total Discriminator loss, and the lower figure shows the total generator loss. There is no significant difference, but the highest learning rate might be prone to outliers. }

@@

	\caption{Generator and Discriminator losses for three different kernel sizes in the convolutional layers. Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}

@@

		\caption{Discriminator loss for different Discriminator training.}

@@

		\caption{Generator losses for different Discriminator training.}

@@

	\caption{The amount of Discriminator training has a high impact on the Discriminator score. The Discriminator repetition indicates the factor by which the Discriminator is trained more with respect to the Generator.}

@@

	\caption{The number of telescopes has a very impact on the model performance. If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other. The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}

@@

Later, GAN extended its version to a conditional model \cite{mirza2014conditional}. In this case, both Generator and Discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) is expressed as:

@@

Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the Generator tries to be close to the ground truth. Hence, the function that is minimized as:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(G)$ is given as
\begin{equation}
	\centering
	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}

@@

\subsection{Generator}
As discussed above, in a GAN, the Generator is responsible for generating fake data; here, the generated images look like real images of a fast-rotating star. The Generator used in this paper is a common U-Net convolutional network \cite{ronneberger2015u}, where the spatial dimension of the image is reduced first using downsampling and then enhanced using upsampling, making it U-shape. The downsampling process typically consists of convolutional layers followed by a strides operation to skip some pixels of the image. Here, the filter is skipping 2 pixels at a time of operation. A leaky version of a Rectified Linear Unit is used to activate the neuron in convolutional layers of the downsampling process.

In contrast, only the Rectified Linear Unit is used to activate the neuron in the upsampling process. The upsampling process also consists of convolutional layers followed by strides = 2 operations to scale up the image for high resolution. However, there is an introduced dropout layer at the beginning of upsampling to avoid over-fitting of the model by the Generator \cite{isola2017image}.

After creating images, the Generator tries to fool the Discriminator into thinking that the generated image is similar to the real image. The level of making fools to Discriminator is called GAN loss. If the Discriminator does not distinguish between the input image and the real image (i.e., the GAN loss is minimum), the Generator stops creating images, and it is trained. However, if the generated image fails to fool the Discriminator, the Generator will again create an image to compare it with the real image. There is another loss calculated by the Generator, which is called L1 loss. It is defined based on the mean absolute error between the pixels of the real image and the generated image. The Generator tries to minimize L1 loss while taking care of GAN loss. The balance between GAN loss and L1 loss allows the Generator to generate realistic yet accurate images.

\subsection{Discriminator}
As discussed before, the Discriminator has the job of classifying the input image by the Generator as real or fake. The Discriminator takes a real image from the data set, also called the target image for the Generator. It tries to train the Generator to create a perfect image while giving feedback based on the input image. Here, the Discriminator that has been taken is PatchGAN \cite{isola2017image}, which does not work globally but rather classifies single patches as real or fake, so it outputs a grid of predictions instead of a single value.

The model architecture of the Discriminator follows the initializer along with inputs (input images and real images). After adding Salt-and-Pepper noise to the input image, PatchGAN focuses on reducing the spatial dimensions of images to extract features, making the model focus on smaller regions of the image. In this process, a leaky version of a Rectified Linear Unit is introduced to convolutional layers as done in the Generator. Later, zero padding adds rows and columns of zeros around the images to prevent loss of spatial information during convolution and extract deeper features from the downsampled output. Now, the Discriminator starts classifying the image as to whether each patch of the input is real or fake based on batch normalization, which normalizes activations to stabilize learning. Later, it goes through LeakyReLU activation, zero-padding, and convolution again and makes a conclusion about the input image, which the Generator takes as feedback.

The quality of the Discriminator is measured based on how it distinguishes between real and fake images, and it is calculated using Discriminator loss. Loss in the Generator helps to train its ability to create better images to fool the Discriminator. Similarly, Discriminator loss helps to train its ability to distinguish between the real image from the dataset and the input image from the Generator. In another way, it actually trains the Generator indirectly. The Discriminator loss is the sum of two losses. The first loss is in distinguishing the real image, which measures how close the Discriminator's predictions for real images are to 1. The second loss is in distinguishing the fake image, which measures how close the Discriminator's predictions for fake images are to 0. The total loss ensures that the Discriminator becomes better at distinguishing real from fake while simultaneously challenging the Generator to produce more realistic images.

### 2024-12-09 Phase_II/draft/II.tex
modification

\section{Intensity Interferometry with Imaging Cherenkov Telescope Array}
Recently, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture). It is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems. R. Hanbury Brown and Robert Q. Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}. Nowadays, Imaging Cherenkov Telescope Arrays (ICTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation. As a result, detection of intensity correlation and angular size measurements of stars is going on for highly resolved imaging with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.

\subsection{The signal for II}\label{sec:signal}
In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}. The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
\begin{equation}
	g^{(2)} = \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
	\label{eqn:HBT}
\end{equation}
where $\tau$ is the time delay between both telescopes. If the light source is chaotic and randomly polarized, we have:
\begin{equation}
	g^{(2)} = 1 + \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eqn:HBT2}
\end{equation}
here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \citep{acciari2020optical}. $V_{12}$ is the Fourier transform of the source brightness distribution and is called complex visibility. Eqn.~\ref{eqn:HBT2} carry the information about the source's structure and shape. However, it loses the phase information due to the presence of only the absolute value of $V_{12}$. In observational astronomy, the correlation in intensity is often expressed in terms of the normalized contrast, given by :
\begin{equation}
	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
\end{equation}
where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ are the mean intensity from two telescopes.

@@

The significance of the signal is expressed as the signal-to-noise ratio (SNR), which depends on many factors. However, most importantly, SNR is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical} 
\begin{equation}
	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma.
	\label{eq:SNR}
\end{equation}
Here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth. The noise of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep{acciari2020optical}. While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with a fixed number of telescopes.  
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/baseline.png}
	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
	\label{fig:base}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
	\caption{This figure shows one of the simulated fast-rotating stars. The brightness is highest at the pole and lowest at the equator due to the presence of high-speed rotation of the star. This effect is named gravitational darkening in astronomy.}
	\label{fig:image}
\end{figure}
\subsection{Baseline considerations}
The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$
\begin{equation}
	V_{12}(B) = \frac{c(B)}{c(0)}.
	\label{eq:angular_size_meas}
\end{equation}
However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}. If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
\begin{equation}
	(u,v) = \frac{1}{\lambda} (B_N, B_E)
\end{equation}
where $B_N$ and $B_E$ are the baselines expressed in north and east coordinates. Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines, which is given as  
\begin{equation}
	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} B_N\\ B_E\\ B_A\\ \end{pmatrix}
	\label{eq:baseline_rot}
\end{equation}
It traces an ellipse for every pair of telescopes. Furthermore, the different altitudes of the telescopes $B_A$ must be considered \citep{dravins2013optical, saha2020theory}. Here, $\delta$ is the declination, and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes. The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}. Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation. Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
\begin{equation}
	\label{eq:N_telescopes}
	\mathcal{N} = \frac{N_T \cdot (N_T -1)}{2}
\end{equation}

As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes. The existing and upcoming Cherenkov Telescope Array Observatory (CTAO) can promise to cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
		\caption{The Fourier transform of the source.}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
		\caption{The logarithmic Fourier transform of the source.}
	\end{subfigure}
	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} on linear and logarithmic scales. Observation of the maximum (u, v) plane with a finite number of baselines can be completed with the help of Earth's rotation.}
	\label{fig:ft}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
		\caption{The Fourier transform with baselines.}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
		\caption{The logarithmic Fourier transform with baselines.}
	\end{subfigure}
	\caption{The upper panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles} on a linear scale, and the lower panel shows the same on a logarithmic scale.}
	\label{fig:ft_base}
\end{figure}
\subsection{An Object: Fast Rotating Stars}
In our work, we simulate a single fast-rotating star to test image reconstruction with II in intersection with the Generative Adversarial Networks (GAN). Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \citep{von1924radiative, 1999A&A...347..185M}. Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object. The brightness is maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}. This effect was first observed in the fast-rotating star Regulus through interferometric and spectroscopic data from the Center for High Angular Resolution Astronomy (CHARA) Array \citep{mcalister2005first}. These stars are crucial for understanding a variety of astrophysical processes and help to understand the stellar evolution, internal structure, and rotational dynamics over time.

Intensity Interferometry (II) detects the photon from the stellar objects, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}). According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky. Fig.~\ref {fig:ft} visualize this statement for the source shown in Fig.~\ref{fig:image} using II on linear and logarithmic scales. However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in Fig.~\ref{fig:ft_base}. It is the covered observational plane using the baselines shown in Fig.~\ref{fig:teles} on linear and logarithmic scales, respectively. However, the instrumentation of existing and upcoming CTAO shows the possibility of covering the maximum observable portion of the visibility plane for stellar objects, offering high resolution to understand the stellar structure and its evolution with time.

>>>>

\section{Intensity Interferometry with Imaging Cherenkov Telescope Array}

R. Hanbury Brown and Robert Q. Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}. After a long gap, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects with high precision levels. It solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture) to reach beyond milli-arc-second. II is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems. Nowadays, Imaging Cherenkov Telescope Arrays (ICTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation. As a result, detection of intensity correlation and angular measurements of stars is going on with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.

\subsection{The Signal with Intensity Interferometry}\label{sec:signal}
In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively. The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
\begin{equation}
	g^{(2)} = \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
	\label{eqn:HBT}
\end{equation}
where $\tau$ is the time delay between both telescopes \citep{acciari2020optical, dravins2013optical}. If the light source is chaotic and randomly polarized, we have:
\begin{equation}
	g^{(2)} = 1 + \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eqn:HBT2}
\end{equation}
here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \citep{acciari2020optical}. $V_{12}$ is the Fourier transform of the source brightness distribution and is called complex visibility. Eqn.~\ref{eqn:HBT2} carry the information about the source's structure and shape. However, it loses the phase information due to the presence of only the absolute value of $V_{12}$. In observational astronomy, the correlation in intensity is often expressed in terms of the normalized contrast, given by :
\begin{equation}
	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
\end{equation}
where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ are the mean intensity from two telescopes.

@@

The significance of the signal is expressed as the signal-to-noise ratio (SNR), which depends on many factors. However, most importantly, SNR is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical} 
\begin{equation}
	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma.
	\label{eq:SNR}
\end{equation}
Here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth. The noise of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep{acciari2020optical}. While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with a fixed number of telescopes.  
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/baseline.png}
	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
	\label{fig:base}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
	\caption{This figure shows one of the simulated fast-rotating stars. The brightness is highest at the pole and lowest at the equator due to the presence of high-speed rotation of the star. This effect is named gravitational darkening in astronomy.}
	\label{fig:image}
\end{figure}

\subsection{Baseline Considerations}
The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$
\begin{equation}
	V_{12}(B) = \frac{c(B)}{c(0)}.
	\label{eq:angular_size_meas}
\end{equation}
However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}. If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
\begin{equation}
	(u,v) = \frac{1}{\lambda} (B_N, B_E)
\end{equation}
where $B_N$ and $B_E$ are the baselines expressed in north and east coordinates. Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines, which is given as  
\begin{equation}
	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} B_N\\ B_E\\ B_A\\ \end{pmatrix}
	\label{eq:baseline_rot}
\end{equation}
It traces an ellipse for every pair of telescopes. Furthermore, the different altitudes of the telescopes $B_A$ must be considered \citep{dravins2013optical, saha2020theory}. Here, $\delta$ is the declination, and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes. The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}. Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (Fig.~\ref{fig:teles}) due to Earth's rotation. Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
\begin{equation}
	\label{eq:N_telescopes}
	\mathcal{N} = \frac{N_T \cdot (N_T -1)}{2}
\end{equation}

As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes. The existing and upcoming Cherenkov Telescope Array Observatory (CTAO) can promise to cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
		\caption{The Fourier transform of the source.}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
		\caption{The logarithmic Fourier transform of the source.}
	\end{subfigure}
	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} on linear and logarithmic scales. Observation of the maximum (u, v) plane with a finite number of baselines can be completed with the help of Earth's rotation.}
	\label{fig:ft}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
		\caption{The Fourier transform with baselines.}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
		\caption{The logarithmic Fourier transform with baselines.}
	\end{subfigure}
	\caption{The upper panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles} on a linear scale, and the lower panel shows the same on a logarithmic scale.}
	\label{fig:ft_base}
\end{figure}

\subsection{An Object: Fast Rotating Stars}
In our work, we simulate a single fast-rotating star to test image reconstruction with II in intersection with the Generative Adversarial Networks (GAN). Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \citep{von1924radiative, 1999A&A...347..185M}. Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object. The brightness is maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}. This effect was first observed in the fast-rotating star Regulus through interferometric and spectroscopic data from the Center for High Angular Resolution Astronomy (CHARA) Array \citep{mcalister2005first}. These stars are crucial for understanding a variety of astrophysical processes and help to understand the internal structure, rotational dynamics, and stellar evolution over time.

Intensity Interferometry (II) detects the photon from the stellar objects, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}). According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky. Fig.~\ref {fig:ft} visualize this statement for the source shown in Fig.~\ref{fig:image} using II on linear and logarithmic scales. However, current observational techniques are unable to capture the full signal, and only partial data can be collected. Fig.~\ref{fig:ft_base} shows the signal on linear and logarithmic scales again for a single night's simulation of II. It is the covered observational plane using the six baselines shown in Fig.~\ref{fig:teles}. However, the instrumentation of existing and upcoming CTAO shows the possibility of covering the maximum observable portion of the visibility plane for stellar objects, offering high resolution to understand the stellar structure and its evolution with time.
